### 2019-07-31 Manuscript.Rmd
Update Manuscript.Rmd

---
title: 
author: Tina & Marc
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_notebook:
    fig_caption: yes
    keep_tex: yes
    highlight: espresso
    number_sections: no
  html_document:
    df_print: paged
  word_document:
    reference_docx: Paper1_reply_v13_Tina_Marc.docx
urlcolor: blue
fontsize: 10pt
geometry: margin=1in
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{float}
- \usepackage{color}
linestretch: 1
bibliography: /Users/admin/Desktop/nwork/simulation/TM.bib
csl: /Users/admin/Desktop/nwork/simulation/styles-master/styles-master/plos.csl 
---

>>>>

---
title: 
author: Tina & Marc
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_notebook:
    fig_caption: yes
    keep_tex: yes
    highlight: espresso
    number_sections: no
  html_document:
    df_print: paged
  word_document:
    reference_docx: Manuscript.docx
urlcolor: blue
fontsize: 10pt
geometry: margin=1in
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{float}
- \usepackage{color}
linestretch: 1
bibliography: /Users/admin/Desktop/nwork/simulation/TM.bib
csl: /Users/admin/Desktop/nwork/simulation/styles-master/styles-master/plos.csl 
---
